---
title: "Tier I AgDrift"
author: "C. Kuan"
date: "Thursday, March 03, 2016"
output: html_document
---

| Aerial | Ground | Airblast |
|--------|--------|----------|
| Preset Model Runs | Field Data Curve Fit | Field Data Curve Fit |
| - 4 Drop Size Classes | - 2 Boom Heights | - 5 Orchard Types |
|                       | - 2 Drop Sizes |                     |
|-----------------------|----------------|---------------------|

# Tier I Aerial

# Tier I Ground
## Low Boom
D(x) = c/(1+ax)^b
where D(x) represents deposition at x downwind distance (ft), and a (ft^-1), b, and c are curve-fitting parameters.

## High Boom
D(x) = (c/(1+ax)^b) * (1+A exp(-Bx)) 
where D(x) represents deposition at x downwind distance (ft), and a (ft^-1), b, and c are curve-fitting parameters. The exponential expression is only for x downwind distance > 25 ft.

```{r, eval=TRUE}
names(df_ground_calc)
```

# Tier I Airblast
D(x) = c/(1+ax)^b
where D(x) represents deposition at x downwind distance (ft), and a (ft^-1), b, and c are curve-fitting parameters.


```{r, eval=TRUE}
names(df_airblast_calc)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
