---
title: "Tier I AgDrift Curve Comparisons"
author: "C. Kuan"
date: "Thursday, March 03, 2016"
output: html_document
---

# Tier I Aerial
- Preset Model Runs with 4 Drop Size Classes
  + Very Fine to Fine
  + Fine to Medium
  + Medium to Coarse
  + Coarse to Very Coarse
  
```{r Tier I Aerial plot, echo=FALSE, fig.width= 10}
## Very fine to fine
par(mfrow=c(1,4), mar=c(2,2,2,2))
plot(df_python$distance_ft, df_python$pond_aerial_vf2f, main = "vf2f", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0, 0.55))
lines(df_aerial_excel$Distance..ft., df_aerial_excel$Very.Fine.to.Fine, lty=2)
legend("topright", c("Python", "Peck"), col = c("black", "black"), lty = c(1, 2), bg = "gray90", cex=1)
## Fine to medium
plot(df_python$distance_ft, df_python$pond_aerial_f2m, col = "red", main = "f2m", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0, 0.55))
lines(df_aerial_excel$Distance..ft., df_aerial_excel$Fine.to.Med, col = "red", lty=2)
legend("topright", c("Python", "Peck"), col = c("red", "red"), lty = c(1, 2), bg = "gray90", cex=1)
## Medium to coarse
plot(df_python$distance_ft, df_python$pond_aerial_m2c, col = "green3", type = "l", main = "m2c", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0, 0.55))
lines(df_aerial_excel$Distance..ft., df_aerial_excel$Med.to.Coarse, col = "green3", lty=2)
legend("topright", c("Python", "Peck"), col = c("green3", "green3"), lty = c(1, 2), bg = "gray90", cex=1)
## Coarse to very coarse
plot(df_python$distance_ft, df_python$pond_aerial_c2vc, col = "blue", type = "l", main = "c2vc", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0, 0.55))
lines(df_aerial_excel$Distance..ft., df_aerial_excel$Coarse.to.VC, col = "blue", lty=2)
legend("topright", c("Python", "Peck"), col = c("blue", "blue"), lty = c(1, 2), bg = "gray90", cex=1)
```

# Tier I Ground
* Field data curve fits with 2 Drop Size Classes at 2 Boom Heights (Low and High)
  + Very Fine to Fine - Low and High
  + Fine to Medium Coarse - Low and High
  
## Low Boom
D(x) = c/(1+ax)^b
where D(x) represents deposition at x downwind distance (ft), and a (ft^-1), b, and c are curve-fitting parameters.

## High Boom
D(x) = (c/(1+ax)^b) * (1+A exp(-Bx)) 
where D(x) represents deposition at x downwind distance (ft), and a (ft^-1), b, and c are curve-fitting parameters. The exponential expression is only for x downwind distance > 25 ft.

```{r Tier I Ground plot, echo=FALSE, fig.width=10}
## Low- very fine to fine
par(mfrow=c(1,4), mar=c(2,2,2,2))
plot(df_ground_calc$distance_ft, df_ground_calc$ground_low_vf2f_90, main = "Low vf2f", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300))
lines(df_ground_excel$Distance..ft., df_ground_excel$Low.boom..vf, lty=2)
lines(df_python$distance_ft, df_python$pond_ground_low_vf2f, lty=4)
legend("topright", c("Calc", "Peck", "Python"), col = c("black", "black", "black"), lty = c(1, 2, 4), bg = "gray90", cex = 1)
## Low- fine to medium coarse
plot(df_ground_calc$distance_ft, df_ground_calc$ground_low_f2mc_90, col = "red", main = "Low f2mc", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300))
lines(df_ground_excel$Distance..ft., df_ground_excel$low.boom..fmc, col = "red", lty=2)
lines(df_python$distance_ft, df_python$pond_ground_low_f2m, col = "red", lty=4)
legend("topright", c("Calc", "Peck", "Python"), col = c("red", "red", "red"), lty = c(1, 2, 4), bg = "gray90", cex = 1)
## High- very fine to fine
plot(df_ground_calc$distance_ft, df_ground_calc$ground_high_vf2f_90, col = "green3", main = "High Vf2f", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300))
lines(df_ground_excel$Distance..ft., df_ground_excel$High.boom..vf, col = "green3", lty=2)
lines(df_python$distance_ft, df_python$pond_ground_high_vf2f, col = "green3", lty=4)
legend("topright", c("Calc", "Peck", "Python"), col = c("green3", "green3", "green3"), lty = c(1, 2, 4), bg = "gray90", cex = 1)
## High- fine to medium coarse
plot(df_ground_calc$distance_ft, df_ground_calc$ground_high_f2mc_90, col = "blue", main = "High f2mc", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300))
lines(df_ground_excel$Distance..ft., df_ground_excel$high.boom..fmc, col = "blue", lty=2)
lines(df_python$distance_ft, df_python$pond_ground_high_f2m, col = "blue", lty=4)
legend("topright", c("Calc", "Peck", "Python"), col = c("blue", "blue", "blue"), lty = c(1, 2, 4), bg = "gray90", cex = 1)
```

# Tier I Airblast
* Field Data Curve Fit with 5 orchard types
  + Orchard
  + Vineyard
  + Normal
  + Dense
  + Sparse

"Inside vs. Outside" refers to whether the treatment was applied inside or outside the rows of trees in the field study
  
D(x) = c/(1+ax)^b
where D(x) represents deposition at x downwind distance (ft), and a (ft^-1), b, and c are curve-fitting parameters.

```{r Tier I Airblast plot, echo=FALSE, fig.width=10}
## orchard
par(mfrow=c(1,5), mar=c(2,2,2,2))
plot(df_airblast_calc$distance_ft, df_airblast_calc$airblast_orchard_inside, main = "Orchard", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition", xlim=c(0,300))
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_orchard_outside, col="blue", lty=2)
lines(df_python$distance_ft, df_python$pond_airblast_orchard, col = "red", lty=2)
lines(df_airblast_excel$Distance..ft., df_airblast_excel$Orchard, col = "green3", lty=2)
legend("topright", c("Calc- inside", "Calc- outside", "Python", "Peck"), col = c("black", "blue", "red", "green3"), lty = c(1, 2, 2, 2), bg = "gray90", cex=1)
## Vineyard
plot(df_airblast_calc$distance_ft, df_airblast_calc$airblast_vineyard_inside, main = "Vineyard", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition", xlim=c(0,300))
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_vineyard_outside, col="blue", lty=2)
lines(df_python$distance_ft, df_python$pond_airblast_vineyard, col = "red", lty=2)
lines(df_airblast_excel$Distance..ft., df_airblast_excel$Vineyard, col = "green3", lty=2)
legend("topright", c("Calc- inside", "Calc- outside", "Python", "Peck"), col = c("black", "blue", "red", "green3"), lty = c(1, 2, 2, 2), bg = "gray90", cex=1)
## Normal
plot(df_airblast_calc$distance_ft, df_airblast_calc$airblast_normal_inside, main = "Normal", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition", xlim=c(0,300))
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_normal_outside, col="blue", lty=2)
lines(df_airblast_excel$Distance..ft., df_airblast_excel$Normal, col = "green3", lty=2)
legend("topright", c("Calc- inside", "Calc- outside", "Peck"), col = c("black", "blue", "green3"), lty = c(1, 2, 2), bg = "gray90", cex = 1)
## Sparse
plot(df_airblast_calc$distance_ft, df_airblast_calc$airblast_sparse_inside, main = "Sparse", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition", xlim=c(0,300))
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_sparse_outside, col="blue", lty=2)
lines(df_airblast_excel$Distance..ft., df_airblast_excel$Sparse, col = "green3", lty=2)
legend("topright", c("Calc- inside", "Calc- outside", "Peck"), col = c("black", "blue", "green3"), lty = c(1, 2, 2), bg = "gray90", cex = 1)
## Dense
plot(df_airblast_calc$distance_ft, df_airblast_calc$airblast_dense_inside, main = "Dense", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition", xlim=c(0,300))
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_dense_outside, col="blue", lty=2)
lines(df_airblast_excel$Distance..ft., df_airblast_excel$Dense, col = "green3", lty=2)
legend("topright", c("Calc- inside", "Calc- outside", "Peck"), col = c("black", "blue", "green3"), lty = c(1, 2, 2), bg = "gray90", cex = 1)
```
