---
title: "Tier I AgDrift Curve Comparisons"
author: "C. Kuan"
date: "Thursday, March 03, 2016"
output: html_document
---
## Data Sources  
  
Source           | Peck Excel | User Manual | agdrift.py | fortran2py.py  
_Plot keyword_   | _Peck_     | _Calc_      | _Python_   | _F2Py_         
-----------------+------------+-------------+------------+--------------  
Aerial vf2f      |x           |             |x           |x               
Aerial f2m       |x           |             |x           |x               
Aerial m2c       |x           |             |x           |x               
Aerial c2vc      |x           |             |x           |x               
Ground high vf2f |x           |x            |x           |x               
Ground high f2m  |x           |x            |x           |x               
Ground low vf2f  |x           |x            |x           |x               
Ground low f2m   |x           |x            |x           |x               
Airblast orchard |x           |x            |x           |x               
Airblast vineyard|x           |x            |x           |x               
Airblast normal  |x           |x            |            |                 
Airblast sparse  |x           |x            |            |                
Airblast dense   |x           |x            |            |                


## Tier I Aerial
* Preset Model Runs with 4 Drop Size Classes
    + Very Fine to Fine
    + Fine to Medium
    + Medium to Coarse
    + Coarse to Very Coarse
  
```{r Tier I Aerial plot, echo=FALSE, fig.width= 10}
## Very Fine to Fine
par(mfrow=c(1,4), mar=c(4,4,1,1))
plot(df_python$distance_ft, df_python$pond_aerial_vf2f, main = "vf2f", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0, 0.55))
lines(df_aerial_excel$Distance..ft., df_aerial_excel$Very.Fine.to.Fine, lty=2)
lines(df_fortran2py$distance_ft, df_fortran2py$Aerial.vf2f, lty = 3)
legend("topright", c("Python", "Peck", "F2Py"), col = c("black", "black", "black"), lty = c(1, 2, 3), bg = "gray90", cex=1)
## Fine to medium
plot(df_python$distance_ft, df_python$pond_aerial_f2m, col = "red", main = "f2m", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0, 0.55))
lines(df_aerial_excel$Distance..ft., df_aerial_excel$Fine.to.Med, col = "red", lty=2)
lines(df_fortran2py$distance_ft, df_fortran2py$Aerial.f2m, col="red", lty=3)
legend("topright", c("Python", "Peck", "F2Py"), col = c("red", "red", "red"), lty = c(1, 2, 3), bg = "gray90", cex=1)
## Medium to coarse
plot(df_python$distance_ft, df_python$pond_aerial_m2c, col = "green3", type = "l", main = "m2c", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0, 0.55))
lines(df_aerial_excel$Distance..ft., df_aerial_excel$Med.to.Coarse, col = "green3", lty=2)
lines(df_fortran2py$distance_ft, df_fortran2py$Aerial.m2c, col="green3", lty=3)
legend("topright", c("Python", "Peck", "F2Py"), col = c("green3", "green3", "green3"), lty = c(1, 2, 3), bg = "gray90", cex=1)
## Coarse to very coarse
plot(df_python$distance_ft, df_python$pond_aerial_c2vc, col = "blue", type = "l", main = "c2vc", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0, 0.55))
lines(df_aerial_excel$Distance..ft., df_aerial_excel$Coarse.to.VC, col = "blue", lty=2)
lines(df_fortran2py$distance_ft, df_fortran2py$aerial.c2vc, col = "blue", lty = 3)
legend("topright", c("Python", "Peck", "F2Py"), col = c("blue", "blue", "blue"), lty = c(1, 2, 3), bg = "gray90", cex=1)
```

***

## Tier I Ground
* Field data curve fits with 2 Drop Size Classes at 2 Boom Heights
    + Very Fine to Fine - Low and High
    + Fine to Medium Coarse - Low and High
  
### Low Boom
A curve-fitting expression to describe the downwind deposition of the 'ground spray' method was developed based on two field studies performed by the Spray Drift Task Force in 1995.   $D(x) = c/(1+ax)^{b}$, where D(x) represents deposition at x downwind distance (ft), and a (ft^-1), b, and c are curve-fitting parameters.

### High Boom
A high-boom model was developed by extending the expression of the low-boom depostion model to:  $D(x) = (c/(1+ax)^{b}) * (1+A exp(-Bx))$, where D(x) represents deposition at x downwind distance (ft), and a (ft^-1), b, and c are curve-fitting parameters. The exponential expression is only for x downwind distance > 25 ft.  

***"Calc 50" and "Calc 90" refer to values in the 50^th^ and 90^th^ percentiles, respectively.***

```{r Tier I Ground plot, echo=FALSE, fig.width=10}
## Low- very fine to fine
par(mfrow=c(1,4), mar=c(4,4,1,1))
plot(df_ground_excel$Distance..ft., df_ground_excel$Low.boom..vf, main = "Low vf2f", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0,0.5))
lines(df_ground_calc$distance_ft, df_ground_calc$ground_low_vf2f_90, lty=2, col = "blue")
lines(df_ground_calc$distance_ft, df_ground_calc$ground_low_vf2f_50, lty=2, col = "green3")
lines(df_fortran2py$distance_ft, df_fortran2py$Ground.low.fine.90, lty=3, col = "red")
lines(df_python$distance_ft, df_python$pond_ground_low_vf2f, lty=4, col = "purple")
legend("topright", c("Peck", "Calc 90", "Calc 50", "F2Py", "Python"), col = c("black", "blue","green3", "red", "purple"), lty = c(1, 2, 2, 3, 4), bg = "gray90", cex = 1)
## Low- fine to medium coarse
plot(df_ground_excel$Distance..ft., df_ground_excel$low.boom..fmc, main = "Low f2mc", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0,0.5))
lines(df_ground_calc$distance_ft, df_ground_calc$ground_low_f2mc_90, col = "blue", lty=2)
lines(df_ground_calc$distance_ft, df_ground_calc$ground_low_f2mc_50, col = "green3", lty=2)
lines(df_fortran2py$distance_ft, df_fortran2py$ground.low.m2c.90, col="red", lty=3)
lines(df_python$distance_ft, df_python$pond_ground_low_f2m, col = "purple", lty=4)
legend("topright", c("Peck", "Calc 90","Calc 50", "F2Py", "Python"), col = c("black", "blue","green3", "red", "purple"), lty = c(1, 2, 2, 3, 4), bg = "gray90", cex = 1)
## High- very fine to fine
plot(df_ground_excel$Distance..ft., df_ground_excel$High.boom..vf, main = "High Vf2f", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0,0.5))
lines(df_ground_calc$distance_ft, df_ground_calc$ground_high_vf2f_90, col = "blue", lty=2)
lines(df_ground_calc$distance_ft, df_ground_calc$ground_high_vf2f_50, col = "green3", lty=2)
lines(df_fortran2py$distance_ft, df_fortran2py$ground.high.fine.90, col="red",lty=3)
lines(df_python$distance_ft, df_python$pond_ground_high_vf2f, col = "purple", lty=4)
legend("topright", c("Peck","Calc 90", "Calc 50", "F2Py", "Python"), col = c("black", "blue","green3", "red", "purple"), lty = c(1, 2, 2, 3, 4), bg = "gray90", cex = 1)
## High- fine to medium coarse
plot(df_ground_excel$Distance..ft., df_ground_excel$high.boom..fmc, main = "High f2mc", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition",xlim=c(0,300), ylim=c(0,0.5))
lines(df_ground_calc$distance_ft, df_ground_calc$ground_high_f2mc_90, col = "blue", lty=2)
lines(df_ground_calc$distance_ft, df_ground_calc$ground_high_f2mc_50, col="green3",lty=2)
lines(df_fortran2py$distance_ft, df_fortran2py$Ground.high.m2c.90, col="red", lty=3)
lines(df_python$distance_ft, df_python$pond_ground_high_f2m, col = "purple", lty=4)
legend("topright", c("Peck", "Calc 90", "Calc 50", "F2Py", "Python"), col = c("black", "blue","green3", "red", "purple"), lty = c(1, 2, 2, 3, 4), bg = "gray90", cex = 1)
```

***

## Tier I Airblast
* Field Data Curve Fit with 5 orchard types
    + Orchard
    + Vineyard
    + Normal
    + Dense
    + Sparse

A curve-fitting expression to describe the downwind deposition of the 'airblast' method was developed based on several field studies performed by the Spray Drift Task Force in 1995.   $D(x) = c/(1+ax)^{b}$, where D(x) represents deposition at x downwind distance (ft), and a (ft^-1), b, and c are curve-fitting parameters. 

***"Inside vs. Outside" refers to whether the treatment was applied inside or outside the rows of trees in the field study.***

```{r Tier I Airblast plot, echo=FALSE, fig.width=10}
## orchard
par(mfrow=c(1,5), mar = c(4,4,1,1))
plot(df_airblast_excel$Distance..ft., df_airblast_excel$Orchard, main = "Orchard", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition", xlim=c(0,300))
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_orchard_outside, col="blue", lty=2)
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_orchard_inside, col = "green3", lty=2)
lines(df_python$distance_ft, df_python$pond_airblast_orchard, col = "red", lty=3)
lines(df_fortran2py$distance_ft, df_fortran2py$Airblast.Orchard.50, col="purple", lty=4)
legend("topright", c("Peck", "Calc Outside", "Calc Inside", "Python", "F2Py"), col = c("black", "blue", "green3", "red", "purple"), lty = c(1, 2, 2, 3, 4), bg = "gray90", cex=1)
## Vineyard
plot(df_airblast_excel$Distance..ft., df_airblast_excel$Vineyard, main = "Vineyard", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition", xlim=c(0,300))
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_vineyard_outside, col="blue", lty=2)
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_vineyard_inside, col = "green3", lty=2)
lines(df_python$distance_ft, df_python$pond_airblast_vineyard, col = "red", lty=3)
lines(df_fortran2py$distance_ft, df_fortran2py$Airblast.vineyard.50, col="purple", lty=4)
legend("topright", c("Peck", "Calc Outside", "Calc Inside", "Python", "F2Py"), col = c("black", "blue", "green3", "red", "purple"), lty = c(1, 2, 2, 3, 4), bg = "gray90", cex=1)
## Normal
plot(df_airblast_excel$Distance..ft., df_airblast_excel$Normal, main = "Normal", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition", xlim=c(0,300))
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_normal_outside, col="blue", lty=2)
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_normal_inside, col = "green3", lty=2)
legend("topright", c("Peck", "Calc Outside", "Calc Inside"), col = c("black", "blue", "green3"), lty = c(1, 2, 2), bg = "gray90", cex = 1)
## Sparse
plot(df_airblast_excel$Distance..ft., df_airblast_excel$Sparse, main = "Sparse", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition", xlim=c(0,300))
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_sparse_outside, col="blue", lty=2)
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_sparse_inside, col = "green3", lty=2)
legend("topright", c("Peck", "Calc Outside", "Calc Inside"), col = c("black", "blue", "green3"), lty = c(1, 2, 2), bg = "gray90", cex = 1)
## Dense
plot(df_airblast_excel$Distance..ft., df_airblast_excel$Dense, main = "Dense", type = "l", xlab = "Distance (ft)", ylab = "Fraction of Deposition", xlim=c(0,300))
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_dense_outside, col="blue", lty=2)
lines(df_airblast_calc$distance_ft, df_airblast_calc$airblast_dense_inside, col = "green3", lty=2)
legend("topright", c("Peck", "Calc Outside", "Calc Inside"), col = c("black", "blue", "green3"), lty = c(1, 2, 2), bg = "gray90", cex = 1)
```
